Legends for Tables

### 2018-11-25 Manuscript/Figures/figure_legends.Rmd
added file for legends of figures/tables

>>>>

# Figure 3: Ensemble Framework/Model Building Pipeline

A diagram of the model building pipeline given an a combination of inputs from the ensemble framework. The data was split into a 7:3 training set to testing set ratio, the variable reduction technique of choice was implemented, and a random forest classification algorithm was performed. Each model was then validated on the same testing set.

# Figure 4: Class Imbalance

Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed. Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.

# Figure 5: 5kb Model Performances

Comparing model performances for TAD boundary data at 5kb resolution across each re-sampling technique. Each square plot represents a random forest classifier performed on 5kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.

# Figure 6: 25kb Model Performances

Comparing model performances for TAD boundary data at 25kb resolution across each re-sampling technique. Each square plot represents a random forest classifier performed on 25kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.

# Figure 7: 50kb Model Performances

Comparing model performances for TAD boundary data at 50kb resolution across each re-sampling technique. Each square plot represents a random forest classifier performed on 50kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.

# Figure 8: 100kb Model Performances

Comparing model performances for TAD boundary data at 100kb resolution across each re-sampling technique. Each square plot represents a random forest classifier performed on 10
+0kb resolution binned boundary data using a particular predictor type, variable reduction algorithm, and re-sampling technique evaluated across 4 different performance metrics.

# Figure 9: Comparing Performances

Comparing performances of random forest classification algorithms, across TAD boundary data at each resolution for models using distance-type predictors, with elastic-net regularization and random under-sampling. Performances were aggregated by taking the average of each metric across 50 iterations of random under-sampling.

# Figure 10: Comparing Variable Importance

Comparing variable importance for the top 15 most predictive functional genomic elements for each of the 4 different resolutions. The x-axis represents the standardized difference between the out-of-bag prediction accuracy after permuting each predictor variable, averaged across all trees. The greater the mean standardized difference, the more importance the predictor is to the model.

### 2018-11-25 Manuscript/Tables/table_legends.Rmd
added file for legends of figures/tables

# Table 2: 5kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 5kb resolution contact matrices.

# Table 3: 25kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 25kb resolution contact matrices.

# Table 4: 50kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 50kb resolution contact matrices.

# Table 5: 100kb Class Distributions

The class distributions for different re-sampling techniques from domain data obtained from 100kb resolution contact matrices.

>>>>

# Table 2: Class Distributions

Summary of the class distributions for each re-sampling technique, across each resolution. All re-sampling techniques yielded completely balanced classes. That is, there was a 1:1 relationship between the majority and minority classes after sampling took place.

# Table 3: 5kb Model Performances

Performance metrics comparing models using different sampling approaches for the 5kb resolution TAD boundary data. The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.

# Table 4: 25kb Model Performances

Performance metrics comparing models using different sampling approaches for the 25kb resolution TAD boundary data. The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.

# Table 5: 50kb Model Performances

Performance metrics comparing models using different sampling approaches for the 50kb resolution TAD boundary data. The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.

# Table 6: 100kb Model Performances

Performance metrics comparing models using different sampling approaches for the 100kb resolution TAD boundary data. The best value in each column for each performance metric is underlined to compare different sampling approaches, while the highest value in each row is highlighted in bold to compare different predictor types.
